Paper 3 - Causal Roadmap

### 2023-04-12 docs/causal_roadmap.qmd
Removed some nodes from DAGs. Fixed some things in roadmap (style mainly). Added more HELIX variables to dictionary mapping.

- \acr{cpm}, for assessing non-verbal intelligence.
- Computerised n-back test, for assessing working memory.
- \acr{ant}.
- \acr{cbcl}, for assessing behavioural and emotional problems.

@@

* \acr{opps}:
  * The \acr{snps} of the *PON1* (paraoxonase 1) gene, known to influence the ability to metabolize and detoxify \acr{opps}: `rs854560` and `rs662`. Reference: https://doi.org/10.1289/ehp.1408976.
  * The \acr{snps} of the genes coding for \acr{opps}-metabolizing enzymes: `rs1803274`, `rs1799807`, `rs662`, `rs854560`, `rs705379`, `rs4244285`, `rs3892097`, and `rs2177180`. Reference: https://doi.org/10.1016/j.chemosphere.2015.07.079.
* Phenols:
  * The \acr{snp} of the *UGT2B15* gene: `rs1902023`. Reference: https://doi.org/10.1016/j.envint.2020.106172.
* Phthalates:
  *  The \acr{snps} of the cytochrome P450 (*CYPs*) and UDP-glucuronosyltransferase (*UGTs*) genes: `rs1057910`, `rs1799853`, `rs4244285`, `rs12248560`, `rs3892097`, `rs1902023`, and `rs11692021`. Reference: https://doi.org/10.1016/j.envint.2021.107046.
  * The \acr{snps} of the *PPAR*$\alpha$ gene: `rs75525202`, `rs4823902`, `rs4253690`, `rs12330015`, `rs5766698`, `rs115250492`, and `rs1800246`. Reference: https://doi.org/10.3389/fgene.2022.855544. Not sure whether these \acr{snps} should be considered in the list below.

>>>>

- \acr{cpm}, for assessing non-verbal intelligence [@RavenCourtRaven:1998]. It includes the following outcomes: sum of the right answers, response time in minutes.
- Computerised n-back test, for assessing working memory [@Kirchner:1958]. The recommended outcome is $d^{\prime}$.
- \acr{ant}, to provide a measure of the efficiency of three different functions of attention [@RuedaFanMcCandliss:2004]. The recommended outcome is \acr{hitrtse}, a measure of response speed consistency.
- \acr{cbcl}, for assessing behavioural and emotional problems [@Tm:2001]. The recommended outcomes are: internalizing scales-emotional problems, externalizing scales-behavioral problems, and total problems.

@@

* \acr{opps}:
  * The \acr{snps} of the *PON1* (paraoxonase 1) gene, known to influence the ability to metabolize and detoxify \acr{opps}: `rs854560` and `rs662`. [Reference](https://doi.org/10.1289/ehp.1408976).
  * The \acr{snps} of the genes coding for \acr{opps}-metabolizing enzymes: `rs1803274`, `rs1799807`, `rs662`, `rs854560`, `rs705379`, `rs4244285`, `rs3892097`, and `rs2177180`. [Reference](https://doi.org/10.1016/j.chemosphere.2015.07.079).
* Phenols:
  * The \acr{snp} of the *UGT2B15* gene: `rs1902023`. [Reference](https://doi.org/10.1016/j.envint.2020.106172).
* Phthalates:
  *  The \acr{snps} of the cytochrome P450 (*CYPs*) and UDP-glucuronosyltransferase (*UGTs*) genes: `rs1057910`, `rs1799853`, `rs4244285`, `rs12248560`, `rs3892097`, `rs1902023`, and `rs11692021`. [Reference](https://doi.org/10.1016/j.envint.2021.107046).
  * The \acr{snps} of the *PPAR*$\alpha$ gene: `rs75525202`, `rs4823902`, `rs4253690`, `rs12330015`, `rs5766698`, `rs115250492`, and `rs1800246`. [Reference](https://doi.org/10.3389/fgene.2022.855544). Not sure whether these \acr{snps} should be considered in the list below.
